### 2023-02-27 paper/content.tex
Minor changes to the figure layout
New version of model setup figure
Includes the observation plane, the sample volume, and other tweaks.
Add R-squared and signal-to-noise ratio in the paper methodology

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{figures/coordinate-system-sketch.png}
\caption{
Schematic representation of the coordinates systems and modelling elements.
The left panel shows the $x, y, z$ right-handed coordinate system with $z$ 
pointing upward and away from the sample. A dipole with dipole moment vector 
$\mathbf{\vec{m}}$ is also shown at coordinates $(x_c, y_c, z_c)$. The 
observation points are located at regular intervals on an $x-y$ plane. 
The right panel zooms in on the dipole and shows the dipole moment vector
expressed in terms of inclination ($I$, positive downwards), declination
($D$, angle with the $\hat{y}$ direction), and moment magnitude
$m = \|\mathbf{m}\|$.
}
\label{fig_coordinate_systems}
\end{figure}

@@

From the main diagonal of $\mathbf{C}$ we can obtain the variances of the
declination $\sigma_D^2$, inclination $\sigma_I^2$, and magnitude $\sigma_m^2$
by propagation of uncertainties

@@

[FALAR SOBRE O CALCULO DE R2]

[INCLUIR A ESTIMATIVA DE NÃO-DIPOLARIDADE]

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=1\linewidth]{figures/simple-synthetic-data.png}
\caption{
  a) Synthetic data contaminated with psedo-random normal noise. b) Individual sources window position (yellow squares) obtained with the blob detection algorithm applied on the total gradient map.
}
\label{fig_synthetic_simple_data}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=0.75\linewidth]{figures/simple-synthetic-dipole-moment.png}
\caption{
  CAPTION NEEDED
}
\label{fig_synthetic_simple_results}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{figures/ComplexSynthetic.png}
\caption{a) Complex synthetic data contaminated with  both high and low frequencies noise. b) Individual sources' window position (yellow squares) obtained with the blob detection algorithm applied on the total gradient map.}
\label{e9td9j9abb}
\end{figure}

>>>>

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/coordinate-system-sketch.png}
\caption{
Schematic representation of the coordinates systems and modelling elements.
The left panel shows the $x, y, z$ right-handed coordinate system with $z$
pointing upward and away from the sample. The top surface of the sample defines
the $z=0$ surface. A dipole with dipole moment vector $\mathbf{\vec{m}}$ is
also shown at coordinates $(x_c, y_c, z_c)$. The observation points are located
at regular intervals on an $x-y$ plane at a positive $z$ separation from the
sample surface. The right panel zooms in on the dipole and shows the dipole
moment vector expressed in terms of inclination ($I$, positive downwards),
declination ($D$, angle with the $\hat{y}$ direction), and moment magnitude $m
= \|\mathbf{m}\|$.
}
\label{fig_coordinate_systems}
\end{figure}

@@

From the main diagonal of $\mathbf{C}$ we can obtain the variances of the
declination $\sigma_D^2$, inclination $\sigma_I^2$, and magnitude $\sigma_m^2$
by the propagation of uncertainties

@@

It is important to note that parameters retrieved during inversion procedures do not always explain the observed data, so it is necessary to evaluate the fitting of the predicted data obtained with these parameters. \cite{Fu2020} apply the calculation of the "non-dipolarity parameter (\emph{D})" by calculating the coefficient of determination ($R^2$, Eq.~\ref{R2}). The latter has a maximum value of 1, if \emph{D} is close enough to this value, a simple dipole model is able to explain the measured data. On the other hand, low values of $R^2$ indicate that the predicted model does not explain the observed data. Some authors \citep[e.g.,][]{Myre2019, CortesOrtuno2021, Lima2009} use another approach for the evaluation of the predicted model, called signal-to-noise ratio (SNR, Eq.~\ref{SNR}). SNR is the trade-off between the signal and its associated noise acquired during the measurement by any sensor. The higher the SNR (in decibels) values the better it will be the fit of the predicted model. For a signal to be “visible”,  \cite{Strum2014} suggest an SNR value of at least 3, which means the signal is 3 times bigger than the noise. Thus, both $R^2$ and SNR techniques are appropriate to be used as a criteria filtering for reliability for dipolar inversions.

\begin{equation}
\label{R2}
\begin{aligned}
\large R^2 = 1 - \frac{ {\left( b_z - {b_{z}}_{dipole} \right)}^2 }{{\left( b_z - \bar{b_z} \right)}^2}
\end{aligned}
\end{equation}

\begin{equation}
\label{SNR}
\begin{aligned}
\large SNR = 10 \log_{10}{\left( \frac{{{\sigma}^2}_{dipole}}{{{\sigma}^2}_{residual}} \right)}
\end{aligned}
\end{equation}

@@

\begin{figure}[!tb]
  \centering
  \includegraphics[width=1\linewidth]{figures/simple-synthetic-data.png}
  \caption{
    Synthetic data and the various processing steps performed prior to the
    dipole moment inversion. 
    a) The synthetic noise-corrupted $b_z$ observations at 
    $z = \qty{5}{\micro\meter}$ due to four dipolar sources with different
    depths and dipole moment vectors 
    (see Table~\ref{tab_synthetic_simple_results}).
    b) The upward-continued data to $z = \qty{10}{\micro\meter}$ showing
    attenuated short-wavelength noise.
    c) The total gradient amplitude (TGA) calculated from the 
    upward-continued data, which is able to concentrate the signal on top
    of each dipolar source. 
    d) The contrast-stretched TGA, highlighting the signal of all four
    sources, including the weak central source.
    e) The detected source bounding boxes (black squares) which correctly
    identify the signal of all four sources.
    f) The estimated source locations (colored circles) from Euler 
    Deconvolution of the upward-continued data inside each bounding box. 
    The color represents the difference between the true and estimated 
    $z$ coordinates.
  }
  \label{fig_synthetic_simple_data}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=0.75\linewidth]{figures/simple-synthetic-dipole-moment.png}
\caption{
  CAPTION NEEDED
}
\label{fig_synthetic_simple_results}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=1\linewidth]{figures/ComplexSynthetic.png}
  \caption{
    a) Complex synthetic data contaminated with  both high and low frequencies noise. b) Individual sources' window position (yellow squares) obtained with the blob detection algorithm applied on the total gradient map.
  }
  \label{e9td9j9abb}
\end{figure}
